### 2013-11-27 manuscripts/reply/reply-figures.tex
Working on reply ms.
Working on section about theory of empirical Bayesian model choice.

\mFigure{../../response-redux/hickerson-et-al-posterior/hickerson-posterior-1k/mean_by_dispersion.pdf}{
    The joint posterior of the mean (\meant{}{}) and dispersion index ($\vmratio{} = 
    \vart{}{}/\meant{}{}$) of divergence times for 22 vertebrate taxon pairs as
    estimated by \citet{Hickerson2013} (see Figure 2B of \citet{Hickerson2013}).
    The posterior samples are color-coded to indicate the erroneous mixture of
    timescales in the analysis of \citet{Hickerson2013};
    grey = $0.05/\mutationRate$ generations and
    black = $0.02/\mutationRate$ generations.
}{figJointPosteriorHickerson}

% \mFigure{../images/coin_flip.pdf}{
%     A plot of three beta probability density functions that represent a prior
%     (black; $beta(0.5, 0.5)$), true posterior (blue; $beta(4.5, 1.5)$), and
%     empirical Bayes density (red; $beta(8.5, 2.5)$) for a dataset of five
%     Bernoulli trials, four of which are successes.
% }{figCoinFlip}

>>>>

\mFigure{../images/coin_flip.pdf}{
    A plot of three beta probability density functions that represent a prior
    (black; $beta(0.5, 0.5)$), true posterior (blue; $beta(4.5, 1.5)$), and
    empirical Bayes density (red; $beta(8.5, 2.5)$) for a dataset of five
    Bernoulli trials, four of which are successes.
}{figCoinFlip}

### 2013-11-27 manuscripts/reply/reply-main.tex
Working on reply ms.
Working on section about theory of empirical Bayesian model choice.

Recently, the journal \emph{Evolution} has served as a medium for a discussion
of potential promises and pitfalls of approximate Bayesian methods of
comparative phylogeographical model choice and prior selection.
The discussion has centered around the model-choice method, \msb
\citep{Huang2011}, which uses approximate Bayesian computation (ABC) to
estimate the temporal distribution of divergences among co-distributed pairs of
taxa by sampling over models of divergence that range from a single
divergence-time parameter (i.e., all pairs of taxa diverged at the same time)
to the fully generalized model in which each pair is assigned a divergence-time
parameter.
A full description of the model is given in \citet{Oaks2012}.

\citet{Oaks2012} published results of simulation-based power analyses showing
that \msb is biased toward inferring models of temporally clustered divergence
times across taxon pairs.
\citet{Hickerson2013} published a response to \citet{Oaks2012} where they
present an empirical Bayesian model-averaging approach that they conclude
circumvents the problems revealed by \citet{Oaks2012}.
These papers are largely in agreement, with \citet{Hickerson2013} reiterating
much of the discussion of \citet{Oaks2012} regarding the impact of broad
uniform priors on Bayesian model choice.
Both papers agree that when broad uniform priors are used to reflect \emph{a
prior} uncertainty about the divergence times of all pairs of taxa under study,
the method can be biased toward inferring biogeographically interesting
scenarios of temporally clustered divergences among taxa (i.e. models with few
divergence-time parameters).
Both papers also agree that this bias toward models with few divergence-time
parameters is due to the much greater parameter space of models with more
divergence-time parameters.
However, the papers disgree about the primary mechanism by which the greater
parameter space of parameter-rich models causes the bias toward clustered
divergence models;
\citet{Oaks2012} suggest a statistical issue is the cause, whereas
\citep{Hickerson2013} prefer a numerical explanation.
% The main areas of disagreement between the papers are centered around
% (1) the mechanism by which broad uniform priors cause the bias of \msb toward
% models with few divergence-time parameters, and
% (2) how to potentially mitigate this issue.

\citet{Oaks2012} suggest the primary cause of the poor behavior of the method
is likely the low marginal likelihoods of parameter-rich models integrated over
vast parameter space with low probability of producing the data, yet relatively
high prior density \citep{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is intrinsic to \msb, concluding the
method's rejection algorithm is inefficient and will be biased
toward models with fewer divergence-time parameters, because the parameter
space of these models are more densely sampled relative to models with more
divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results of additional analyses that, when combined with
the results of \citet{Oaks2012}, strongly suggest small marginal likelihoods of
models with more parameter space is a primary mechanism by which uniform priors
are causing the bias of \msb.

@@

There is also some disagreement between the papers also regarding potential
solutions to the bias.
\citet{Oaks2012} suggest alternative prior probability distributions on
divergence-times and other nuisance parameters could increase the marginal
likelihoods of models with more divergence-time parameters and thus reduce the
bias.
Alternatively, \citet{Hickerson2013} present an approach that uses empirically
informed priors and Bayesian model-averaging in an attempt to accommodate
uncertainty in selecting priors.
\citet{Hickerson2013} champion this strategy as a means of avoiding the
pitfalls raised by \citet{Oaks2012}.
In general, we agree with the use of Bayesian model averaging to obtain a
posterior estimate marginalized over uncertainty in prior choice.
However, we question whether adding an additional dimension of model choice
that samples over empirically informed uniform priors is a fruitful solution
for an already biased model-choice method.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different time units, which makes the results presented
in their response difficult to interpret (see Supporting Information for
details).
However, here we show that even when that error is avoided, the empirical
Bayesian model-averaging approach of \citet{Hickerson2013} remains biased
toward clustered divergence models, and is predisposed to excluding true
parameter space.
Their approach provides another means by which the model can ``escape'' large
parameter space, and the method's bias toward smaller models remains.
Importantly, this bias can manifest by preferring narrow, empirically informed
priors that exclude true parameter space.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice.

@@

% \cwlnote{}{This part seems important, but not related to the error in units
% discussed above}
Another important characteristic of the approach used by \citet{Hickerson2013}
that makes their results difficult to interpret is their use of narrow,
empirically guided uniform priors in an approximate-Bayesian model-choice
framework.
We discuss the risks associated with this approach in the next section, and
show how the results of \citet{Hickerson2013} likely exclude true values of the
model's parameters.

@@

\section*{The potential implications of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected.''
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors to reflect the large amount of uncertainty about the
model's parameters for their study system (see their section ``Specifying and
simulating the joint prior'').
\citet{Oaks2012} further discuss how the use of uniform prior distributions in
\msb for many of the model's parameters requires investigators to select broad
priors to avoid excluding the truth \textit{a priori}, and how these broad
uniform priors place too much density in improbable regions of parameter space.
What \citet{Hickerson2013} mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and the power of \msb under real-world
situations when a large amount of prior information is available. 
In doing so, \citet{Oaks2012} discuss
the potential dangers of taking an empirical Bayesian approach to model choice
(see the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}), and we expand on this here by exploring both the theoretical
and practical implications of using empirically informed priors for Bayesian
model choice.

@@

Thus, empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and incorrectly shaped;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
This is not to say that empirical Bayesian approaches are not useful.
Empirical Bayes is a well-studied branch of Bayesian statistics that has given
rise to many powerful inference methods that provide powerful means of
parameter estimation that often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is questionable.
In Bayesian model choice, the primary goal is not to estimate parameters, but
to estimate the relative probabilities of candidate models.
In a simple example of Bayesian model choice where two candidate models, $M_1$
and $M_2$, are being compared, the goal is to estimate the posterior
probabilities of these two models.
Again, we can use Bayes' rule to calculate this as
\begin{equation}
    p(M_1 \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given
    M_1)p(M_1)}{p(\alignment{i}{} \given M_1)p(M_1) + p(\alignment{i}{} \given
    M_2)p(M_2)}.
    \label{eq:bayesmodelchoice}
\end{equation}
By comparing Equations \ref{eq:bayesrule} and \ref{eq:bayesmodelchoice}, we
can see the fundamental differences between Bayesian parameter estimation and
model choice.
In Equation \ref{eq:bayesrule}, we can see that the posterior density of any
state $\myTheta{}$ of the model, is the prior density updated by the
probabiliity of the data given the state $\myTheta{}$ (the likelihood of
$\myTheta{}$).
The integral over the entire parameter space of the model, which is defined by
the priors, only appears as a normalizing constant in the denominator.
Thus, as long as the joint prior distribution contains the values of $\myTheta{}$
that maximize the probability of the data (i.e., the maximum likelihood) and the
data are strongly informative relative to the prior, the modes of the parameter
estimates will be relatively robust to prior choice, even if the shape of the
posterior is incorrect due to using the data to inform the priors.
This is why empirical Bayes can work well for estimating the values of model
parameters.

However, if we look at Equation~\ref{eq:bayesmodelchoice}, we see that in
Bayesian model choice it is now the \emph{marginal} likelihood of a model
the updates the prior probability of that model to yield posterior
probability.
Thus the integral over the entire parameter space of the likelihood weighted by
the prior probability density is no longer a normalizing constant, but rather
is what informs the posterior probability of that model from the data.
As a result, Bayesian model choice tends to be much more sensitive to priors
than Bayesian parameter estimation.
Another important difference of Bayesian model choice that is illustrated by
Equations~\ref{eq:bayesmodelchoice} is that the value of interest, the
posterior probability of a model, is not a parameter of the model, but rather a
single value that is a summary of the entire posterior distribution.
This further complicates the meaning of model posterior probabilities when
Bayes' rule is violated by empirically informing model priors.
Model posterior probabilities are inherently measures of our belief in
the models after our prior beliefs are updated by the data being analyzed.
Unlike model parameters, there are no true values for model probabilities,
and there are no measures of uncertainty in the posterior estimates. 
For empirical Bayesian parameter estimation, the hope is that by giving the
data more weight relative to the prior, the posterior distribution will be
peaked near the true value(s) of the model's parameter(s).
There is no such justification for empirical Bayesian model choice, because
there are no true model probabilities that we are trying to estimate.
Rather using the data twice will simply mislead our posterior
beliefs in the models being compared.

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the probability of a particular coin
being weighted toward landing heads.
We already have data from flipping a different coin 20 times
that landed both heads and tails 10 times, and so we decide to use
these data in specifying a beta prior on fairness of the new coin of
$beta(a=10, b=10)$ (Figure~\ref{figCoinFlip}).

@@

Unlike parameter estimates, posterior probabilities represent a summary of the
entire posterior distribution.
Thus, given that empirical Bayesian posterior distributions are not accurate,
there is no guarantee regarding the accuracy of probabilities summarized from
them.

Equation~\ref{eq:bayesrule} above shows Bayes rule for calculating the
posterior distributions of the parameter(s) of some model $M$, and thus
represents Bayesian parameter estimation given model $M$
We can add the implicit notation for the model $M$ being used to
the marginal likelihood in Equation~\ref{eq:marginallikelhiood} to get
\begin{equation}
    p(\alignment{i}{} \given M) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M) d\myTheta{}.
    \label{eq:marginallikelhioodexpanded}
\end{equation}
In a simple example of Bayesian model choice where two candidate models, $M_1$
and $M_2$, are being compared, the posterior probability of $M_1$ is
\begin{equation}
    p(M_1 \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given
    M_1)p(M_1)}{p(\alignment{i}{} \given M_1)p(M_1) + p(\alignment{i}{} \given
    M_2)p(M_2)}.
    \label{eq:bayesmodelchoice}
\end{equation}

In addition to these theoretical concerns there are practical dangers to using
narrow, empirical, uniform priors for a method that has already been shown to
be biased toward models with less parameter space.
% %CWL:
% %I like the example, but it may be too cute. It is also too long. I think a
% %contrived example is good, but if there could be an example that is more
% %relevant to model choice and comparison of inaccurate posterior distributions,
% %I think that would be better. This is an example of empirical Bayes, but not
% %the potential problem with the use in msbayes. Unless I am interpreting wrong.
% %I would be careful about making it to cute as well. You may intend to make it
% %easy to understand for a general audience, but it can also seem like talking
% %down to Hickerson et al, who we are responding to. It just depends on how you
% %read it.
% This can be demonstrated with a simple, albeit contrived, example.
% Let us say that principal investigator Mary and her new postdoc Will are
% interested in the hypothesis that the mass of George Washington's periwig
% renders the quarter dollar of the United States unfair.
% That is to say their null hypothesis is that the probability of a US
% quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
% They can certainly evaluate this hypothesis, they can have undergraduate
% worker, Joe, flip the coin for them while they tabulate the results.
% But being Bayesians, before they call Joe into the lab, they agree on a
% prior probability to place on the set of all possible probabilities that
% the quarter will land heads when it is flipped.
% Given that neither of them have a quarter, and their prior knowledge that Joe
% moonlights as a magician, and is notorious for performing coin and card tricks
% in the lab, they suspect there is a good chance that the quarter Joe uses will
% be either two-headed or two-tailed.
% So, knowing that the beta distribution is the conjugate prior for a binomial
% likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
% (Figure~\ref{figCoinFlip}).

>>>>

Recently, the journal \emph{Evolution} has served as a medium for a discussion
of potential promises and pitfalls of approximate-Bayesian methods of
comparative phylogeographical model choice and prior selection.
The discussion has centered around the model-choice method, \msb
\citep{Huang2011}, which uses approximate Bayesian computation (ABC) to
estimate the temporal distribution of divergences among co-distributed pairs of
taxa by sampling over models of divergence that range from a single
divergence-time parameter (i.e., all pairs of taxa diverged at the same time)
to the fully generalized model in which each pair is assigned a divergence-time
parameter.
A full description of the model is given in \citet{Oaks2012}.

\citet{Oaks2012} published results of simulation-based power analyses showing
that \msb is biased toward inferring models of temporally clustered divergence
times across taxon pairs.
\citet{Hickerson2013} published a response to \citet{Oaks2012} where they
present an empirical Bayesian model-averaging approach that they conclude
circumvents the problems revealed by \citet{Oaks2012}.
These papers are largely in agreement, with \citet{Hickerson2013} reiterating
much of the discussion of \citet{Oaks2012} regarding the impact of broad
uniform priors on Bayesian model choice.
Both papers agree that when broad uniform priors are used to reflect \emph{a
prior} uncertainty about divergence times of all pairs of taxa under study,
the method can be biased toward inferring biogeographically interesting
scenarios of temporally clustered divergences among taxa (i.e. models with few
divergence-time parameters).
Both papers also agree that this bias toward models with few divergence-time
parameters is due to the much greater parameter space of models with more
divergence-time parameters.
However, the papers disgree about the primary mechanism by which the greater
parameter space of parameter-rich models causes the bias toward clustered
divergence models;
\citet{Oaks2012} suggest a statistical issue is the cause, whereas
\citep{Hickerson2013} prefer a numerical explanation.
% The main areas of disagreement between the papers are centered around
% (1) the mechanism by which broad uniform priors cause the bias of \msb toward
% models with few divergence-time parameters, and
% (2) how to potentially mitigate this issue.

\citet{Oaks2012} suggest the primary cause of the bias of \msb is the low
marginal likelihoods of parameter-rich models integrated over vast parameter
space with low probability of producing the data, yet relatively high prior
density \citep{Lindley1957} imposed by the uniformly distributed prior on
divergence times.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is intrinsic to \msb, concluding the
method's rejection algorithm is inefficient and will be biased
toward models with fewer divergence-time parameters, because the parameter
space of these models are more densely sampled relative to models with more
divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results of additional analyses that, when combined with
the results of \citet{Oaks2012}, strongly suggest small marginal likelihoods of
models with more parameter space is a primary mechanism by which uniform priors
are causing the bias of \msb.

@@

There are also differences between the papers regarding potential solutions to
the bias.
\citet{Oaks2012} suggest alternative prior probability distributions on
divergence-times and other nuisance parameters could increase the marginal
likelihoods of models with more divergence-time parameters and thus reduce the
bias.
Alternatively, \citet{Hickerson2013} present an approach that uses empirically
informed priors and Bayesian model-averaging in an attempt to accommodate
uncertainty in selecting priors.
% \citet{Hickerson2013} champion this strategy as a means of avoiding the
% pitfalls raised by \citet{Oaks2012}.
In general, we agree with the use of Bayesian model averaging to obtain a
posterior estimate marginalized over uncertainty in prior choice.
However, we question whether adding an additional dimension of model choice
that samples over empirically informed uniform priors is a fruitful solution
for an already biased model-choice method.

In this paper, we discuss the potential theoretical and practical problems of
using empirically informed priors for Bayesian model choice.
Furthermore, we evaluate the empirical Bayesian model averaging approach of
\citet{Hickerson2013} as a potential solution to the biases revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different time units, which makes the results presented
in their response difficult to interpret (see Supporting Information for
details).
However, here we show that even when that error is avoided, the empirical
Bayesian model-averaging approach of \citet{Hickerson2013} remains biased
toward clustered divergence models, and is predisposed to excluding true
parameter space.
The approach provides another means by which the method can ``escape'' models
with large parameter space, and the method's bias toward smaller models
remains.
Importantly, this bias can manifest by preferring narrow, empirically informed
priors that exclude true parameter space.

@@

% \cwlnote{}{This part seems important, but not related to the error in units
% discussed above}
% Another important characteristic of the approach used by \citet{Hickerson2013}
% that makes their results difficult to interpret is their use of narrow,
% empirically guided uniform priors in an approximate-Bayesian model-choice
% framework.
% We discuss the risks associated with this approach in the next section, and
% show how the results of \citet{Hickerson2013} likely exclude true values of the
% model's parameters.

@@

\section*{The potential implications of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected.''
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors to reflect the large amount of uncertainty about the
model's parameters for their study system (see section ``Specifying and
simulating the joint prior'' of \citet{Oaks2012}).
\citet{Oaks2012} further discuss how the use of uniform prior distributions in
\msb for many of the model's parameters requires investigators to select broad
priors to avoid excluding the truth \textit{a priori}, and how these broad
uniform priors place too much density in improbable regions of parameter space.
What \citet{Hickerson2013} mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and the power of \msb under real-world
situations when a large amount of prior information is available. 
In doing so, \citet{Oaks2012} discuss the potential dangers of taking an
empirical Bayesian approach to model choice (see the last paragraph of
``Assessing prior sensitivity of \msb'' in \citet{Oaks2012}), and we expand on
this here by exploring both the theoretical and practical implications of using
empirically informed priors for Bayesian model choice.

@@

Thus, empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and incorrectly shaped;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
This is not to say that empirical Bayesian approaches are not useful.
Empirical Bayes is a well-studied branch of Bayesian statistics that has given
rise to many inference methods that provide means of
parameter estimation that often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is questionable.
In Bayesian model choice, the primary goal is not to estimate parameters, but
to estimate the relative probabilities of candidate models.
In a simple example where two candidate models, $M_1$ and $M_2$, are being
compared, the goal is to estimate the posterior probabilities of these two
models.
Again, we can use Bayes' rule to calculate this as
\begin{equation}
    p(M_1 \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given
    M_1)p(M_1)}{p(\alignment{i}{} \given M_1)p(M_1) + p(\alignment{i}{} \given
    M_2)p(M_2)}.
    \label{eq:bayesmodelchoice}
\end{equation}
By comparing Equations \ref{eq:bayesrule} and \ref{eq:bayesmodelchoice}, we
see fundamental differences between Bayesian parameter estimation and
model choice.
In Equation \ref{eq:bayesrule}, we see that the posterior density of any
state $\myTheta{}$ of the model, is the prior density updated by the
probability of the data given the state $\myTheta{}$ (the likelihood of
$\myTheta{}$).
The integral over the entire parameter space of the model, which is defined by
the priors, only appears as a normalizing constant in the denominator.
Thus, as long as the joint prior distribution contains the values of
$\myTheta{}$ that maximize the probability of the data (i.e., the maximum
likelihood) and the data are strongly informative relative to the prior, the
modes of the estimated posterior distributions of parameters will be relatively
robust to prior choice, even if the shape of the posterior is incorrect due to
using the data to inform the priors.
This is why empirical Bayes can work well for estimating the values of model
parameters.

% Unlike parameter estimates, posterior probabilities represent a summary of the
% entire posterior distribution.
% Thus, given that empirical Bayesian posterior distributions are not accurate,
% there is no guarantee regarding the accuracy of probabilities summarized from
% them.

However, if we look at Equation~\ref{eq:bayesmodelchoice}, we see that in
Bayesian model choice it is now the \emph{marginal} likelihood of a model the
updates the prior to yield the model's posterior probability.
Thus the integral over the entire parameter space of the likelihood weighted by
the prior probability density is no longer a normalizing constant, but rather
is what informs the posterior probability of that model from the data.
As a result, Bayesian model choice tends to be much more sensitive to priors
than Bayesian parameter estimation.

Another important difference of Bayesian model choice illustrated by
Equation~\ref{eq:bayesmodelchoice} is that the value of interest, the
posterior probability of a model, is not a function of \myTheta{}, because
it is integrated out of the marginal likelihoods of the candidate models.
Thus, unlike parameter estimates, the estimated posterior probability of a
model is a single value (rather than a distribution) lacking a measure of
posterior uncertainty, and in most cases has no true value.
In most empirical applications, we know all candidate models are incorrect, but
our goal is to summarize the relative probabilities that they could produce the
observed data.
Model posterior probabilities are inherently measures of our belief in the
models after our prior beliefs are updated by the data being analyzed.

This complicates the meaning of model posterior probabilities when Bayes' rule
is violated by empirically informing priors.
For empirical Bayesian parameter estimation, the objective is that by giving the
data more weight relative to the prior, the posterior distribution will be
peaked near the true value(s) of the model's parameter(s).
There is no such justification for empirical Bayesian model choice, because
there are no true values for the model probabilities being estimated.
Using the data twice will simply mislead our posterior beliefs in the models
being compared.

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the probability of a particular coin being
weighted toward landing heads (i.e., $p(p(heads) > 0.5)$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times, and so we decide to use these data in specifying a
beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin $N=10$ times, $y=3$ of which land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$;
this is the true posterior distribution of $\theta$ given our prior information
and data (Figure~\ref{figCoinFlip}).
Thus, the posterior mode estimate of the probability of heads is 0.429, and the
posterior probability of our hypothesis is then $p(p(heads) > 0.5 \given
heads=3, N=10) = 0.23$.
To give the data more weight relative to the prior, we could use it twice, and
calculate an empirical Bayes estimate using a prior of $beta(13,17)$.  This
results in a distribution of $beta(16, 24)$ (Figure~\ref{figCoinFlip}), with a
mode of 0.395, and the $p(p(heads) > 0.5 \given heads=3, N=10) = 0.10$.
Whereas the estimate of the parameter $p(heads)$ is a distribution, the mode of
which changed only 8\% under the empirically informed prior, the posterior
probability of our model of interest ($p(p(heads) > 0.5)$) is a single value,
which changed by 56\% under the empirical prior.
From this example, we can see how Bayesian model choice is more sensitive
to priors, and how using the data twice can mislead the posterior
probability of a model in light of new data.

In addition to these theoretical concerns there are practical problems with
using narrow, empirical, uniform priors for a method that has already been
shown to be biased toward models with less parameter space.

@@

% %CWL:
% %I like the example, but it may be too cute. It is also too long. I think a
% %contrived example is good, but if there could be an example that is more
% %relevant to model choice and comparison of inaccurate posterior distributions,
% %I think that would be better. This is an example of empirical Bayes, but not
% %the potential problem with the use in msbayes. Unless I am interpreting wrong.
% %I would be careful about making it to cute as well. You may intend to make it
% %easy to understand for a general audience, but it can also seem like talking
% %down to Hickerson et al, who we are responding to. It just depends on how you
% %read it.
% This can be demonstrated with a simple, albeit contrived, example.
% Let us say that principal investigator Mary and her new postdoc Will are
% interested in the hypothesis that the mass of George Washington's periwig
% renders the quarter dollar of the United States unfair.
% That is to say their null hypothesis is that the probability of a US
% quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
% They can certainly evaluate this hypothesis, they can have undergraduate
% worker, Joe, flip the coin for them while they tabulate the results.
% But being Bayesians, before they call Joe into the lab, they agree on a
% prior probability to place on the set of all possible probabilities that
% the quarter will land heads when it is flipped.
% Given that neither of them have a quarter, and their prior knowledge that Joe
% moonlights as a magician, and is notorious for performing coin and card tricks
% in the lab, they suspect there is a good chance that the quarter Joe uses will
% be either two-headed or two-tailed.
% So, knowing that the beta distribution is the conjugate prior for a binomial
% likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
% (Figure~\ref{figCoinFlip}).
